Characterization of gaps in directly bonded Si compound optics

### 2014-02-17 AO_bondedSi.tex
add table of measurement outcomes interpretation

\begin{figure}[htbp]
\centerline{\includegraphics[width=.8\columnwidth]{figs/20130911_VS21posM1.eps}}
\caption{IR transmission spectrum of VS21 (M1) showing consistent gap\label{VS21specm1}.  Example spectrum through part VS21 at a position through the mesh gap of known dimensions.}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=.8\columnwidth]{figs/20130911_VS21posF1.eps}}
\caption{IR transmission spectrum of part VS21 (F1) showing evidence for an excess gap\label{VS21specf1}.  Example spectrum through part VS21 at a position through the mesh gap of known dimensions.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=.8\columnwidth]{figs/20130911_VS21posM1}}
\caption{IR transmission spectrum of VS21 (M1) showing consistent gap\label{VS21specm1}.  Example spectrum through part VS21 at a position through the mesh gap of known dimensions.}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=.8\columnwidth]{figs/20130911_VS21posF1}}
\caption{IR transmission spectrum of part VS21 (F1) showing evidence for an excess gap\label{VS21specf1}.  Example spectrum through part VS21 at a position through the mesh gap of known dimensions.}
\end{figure}

\begin{table}[h!]
  \caption{A simple table}
  \begin{center}
    \begin{tabular}{ccc}
    \hline
    Appearance of spectra & Interpretation & Exemplar \\
    \hline
    Measurement within the prediction band & Life is good & VS21-M1, Figure \ref{VS21specm1}\\
    Measured spectrum below the prediction band but shape is similar & Gap was slightly larger than predicted or bonding was incomplete& VS21-F1, Figure \ref{VS21specf1}\\
    Measured spectrum above the prediction band but shape is similar & Gap was slightly smaller than predicted & VS21-M2\\
    Measured spectrum exceeds DSP reference puck & unanticipated anti-reflection coating on the surface of the Si sample (e.g. Sharpie marker residue) & -\\
    High frequency, low amplitude wiggles superimposed upon smooth underlying trend & Large, unanticipated gap, with a small fill factor  & VS21-C3\\   
     																			     & wavelength dependent diffraction from the mesh patterns & VS21-C3\\       
     																			     & measurement artifact  & VS21-C3\\       												
    Non-unit transmission constant with wavelength (gray spectrum) & Artifact of measurement- vignetting of beam, absorptive coating, zero-point drift & VS21-C4 \\
    \hline
    \end{tabular}
  \end{center}
\end{table}
